\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\subsection{Model Validation}

@@

One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A square shape formation consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, that at a solid boundary, the fluid will have zero velocity relative to the boundary. The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary.. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

@@

In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. The velocity magnitute is builded up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant. An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
\subfigure[flow at t=250]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
\subfigure[flow at t=3000]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{center}
\end{figure}

 The purpose of these case was to verify that our model is working for cases that experimentally are proven. This will allow to proceed further and expand this technique into more complex formations. A more detailed description of the element type and the formation that will be used in the next set of test cases follows.

\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}

@@

\begin{figure}[h]
\begin{center}
\subfigure[The $P_{1}DGP_{2}$ element type]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type.pdf}
}%
\subfigure[The map of permeabilities]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}\\
\end{center}
\caption{(a) represents the element type of $P_{1}DGP_{2}$ as well as where each of the parameters is located and calculated on the element type. (b) describes the permeability map as this is introduced throught a python script during the set-up of simulations. In general, the main body of the formation is the blue area that is fully saturated with fluid $2$. Above the main (blue colored) area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio. All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.   }
\label{fig:elem_type_perm_map}
\end{figure}

>>>>

%%%%%%%%%%%%
\subsection{Model Validation}

@@

\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}. A square shape formation consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas). The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied, that at a solid boundary, the fluid will have zero velocity relative to the boundary. The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary.. The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and develops. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.

@@

\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. The velocity magnitute is builded up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant. An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
\subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{center}
\end{figure}

 The purpose of these cases was to verify that our model is working for cases that experimentally are proven. This will allow to proceed further and expand this technique into more complex formations. A more detailed description of the element type and the formation that will be used in the next set of test cases follows.

%%%%%%%%%%%%
\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}

@@

Having already verified that model is working for the test-cases illustrated in previous section, its to introduce a more complicated case where we have regions of different geometrical domains and different permeabilities. The time, the domain that we will use is defined in fig.\ref{fig:testcase_heter_domain}.

\begin{figure}[h]
\begin{center}

\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{a}}

\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase_heter_domain}
\end{center}
\end{figure}
